\documentclass[11pt]{article}

% Edit this customize for an instructor

\newcommand{\instructorpronoun}[1]{his}

% Use this when displaying a new command

\newcommand{\command}[1]{``\lstinline{#1}''}
\newcommand{\program}[1]{\lstinline{#1}}
\newcommand{\url}[1]{\lstinline{#1}}
\newcommand{\channel}[1]{\lstinline{#1}}
\newcommand{\option}[1]{``{#1}''}
\newcommand{\step}[1]{``{#1}''}

\usepackage{pifont}
\newcommand{\checkmark}{\ding{51}}
\newcommand{\naughtmark}{\ding{55}}

\usepackage{listings}
\lstset{
  basicstyle=\small\ttfamily,
  columns=flexible,
  breaklines=true
}

% Define the headers and footers

\usepackage{fancyhdr}

\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}

\pagestyle{fancy}

\fancyhf{}
\rhead{Computer Science 302}
\lhead{Syllabus}
\rfoot{Page \thepage}
\lfoot{Spring 2019}

% Use elastic spacing around the headers

\usepackage{titlesec}
\titlespacing\section{0pt}{6pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

\newcommand{\syllabustitle}[1]
{
  \begin{center}
    \begin{center}
      \bf
      CMPSC 302\\Web Development\\
      Spring 2019\\
      \medskip
    \end{center}
    \bf
    #1
  \end{center}
}

\begin{document}

\thispagestyle{empty}

\syllabustitle{Syllabus}

% \vspace*{-2em}
\subsection*{Course Instructor}
Dr.\ Gregory M.\ Kapfhammer\\
\noindent Office Location: Alden Hall 108 \\
\noindent Office Phone: +1 814--332--2880 \\
\noindent Email: \url{gkapfham@allegheny.edu} \\
\noindent Twitter: \url{@GregKapfhammer} \\
\noindent Web Site: \url{https://www.gregorykapfhammer.com/}

\subsection*{Instructor's Office Hours}

\begin{itemize}

  \itemsep0em

  \item Wednesday: 10:00 am--11:00 am and 2:30 pm--3:30 pm (15 minute time slots)

  \item Thursday: 11:00 am--12:00 noon and 2:30 pm--3:30 pm (15 minute time slots)

  \item Friday: 10:00 am--11:00 am and 11:00--12:00 noon (15 minute time slots)

\end{itemize}

\vspace*{-.05in}

\noindent To schedule a meeting with me during my office hours, please visit my
web site and click the ``About $\rightarrow$ Schedule'' link in the top
left-hand corner. Now, you can browse my office hours or schedule an appointment
by clicking the correct link and then reserving an open time slot. Students are
also encouraged to post appropriate questions to a channel in Slack, which is
available at \url{https://CMPSC302Spring2019.slack.com/}, and monitored by the
instructor and the teaching assistants.

\vspace*{-.1in}

\subsection*{Course Meeting Schedule}

Lecture, Discussion, and Group Work Session: Monday and Wednesday 9:00 am--9:50 am \\
Practical Session: Friday 9:00 am--9:50 am \\
Laboratory Session: Monday, 2:30 pm--4:20 pm \\
Final Examination: Thursday, May 2, 2019 at 9:00 am

\subsection*{Course Description}

\begin{quote}

An introduction to the principles and applications of computer science with an
emphasis on understanding intercultural perspectives that arise during the
design, implementation, and maintenance of mobile-ready web sites. Participating
in hands-on activities that often require teamwork, students learn the
computational methods needed to create web sites that are useful to people from
different cultures and nationalities. Students also investigate approaches to
developing efficient, accessible, and aesthetically pleasing web sites that
adhere to the international standards set by the World Wide Web Consortium.
During a weekly laboratory session students use state-of-the-art web development
technologies to complete projects, reporting on their results through both
written documents and oral presentations. Prerequisite: FS 102 or permission of
the instructor. Distribution Requirements: IP, SP. \@ \\

\end{quote}

\noindent Students can access the course's web site by visiting the instructor's
site, clicking the ``Courses'' link in the top left-hand corner, and looking for
the name and number of this course in the listing.

\subsection*{Course Objectives}

The process of designing, implementing, testing, and deploying correct and
efficient web sites involves the application of many interesting theories,
techniques, and tools. In addition to introducing problem solving and
computational thinking skills, this course will teach students how to create
mobile-ready web sites that are accessible to individuals from different
cultures and nationalities. Using the Git version control system, students will
learn how to develop web sites with Markdown, JavaScript, the hypertext markup
language (HTML), cascading style sheets (CSS), and other web languages.
%
Students will gain hands-on experience in the use, design, implementation, and
testing of web sites during the completion of laboratory and practical
assignments and a design portfolio. Along with learning more about how to
effectively work in a team of diverse web developers, students will enhance
their ability to write and present ideas about web-based software in a clear and
compelling fashion. Students will also develop an understanding of the
connections between computer science, web sites, and other disciplines in the
social and natural sciences and the humanities.

\subsection*{Performance Objectives}

At the completion of this semester, students must have a strong grasp of the
basic features in programming languages used for web development and an
ever-deepening knowledge of topics like responsive web design. Also, students
should be able to handle many of the important, yet accidental, aspects of web
development. That is, students should be comfortable with using a text editor
and understand how to use software tools such a GitHub and GatorGrader. Students
should have a toolkit of constructs in web development languages that they can
use to respond to the challenges that they encounter during the design,
creation, testing, and evaluation of a web site. Students should also be
familiar with how the standards of the World Wide Web Consortium influence the
creation of mobile-ready web sites that are accessible to individuals from
diverse backgrounds. Finally, students should demonstrate the ability to use
both in-person discussions and cutting-edge software tools to effectively
communicate and collaborate with a group of diverse team members.

\subsection*{Required Textbook}

\noindent{\em Fundamentals of Web Development}. Randy Connolly and Ricardo Hoar,
Second Edition, ISBN--10:\ 0134481267, ISBN--13:\ 978--01334481265, 1184 pages, 2017. \\
(References to the textbook are abbreviated as ``FWD'' on the course web site and the syllabus).

\vspace*{.1in}

\noindent
Students who want to improve their technical writing skills may consult the following books.

\vspace*{.1in}

\noindent{\em BUGS in Writing: A Guide to Debugging Your Prose}. Lyn Dupr\'e. Second Edition,  ISBN--10: 020137921X,
ISBN-13: 978--0201379211, 704 pages, 1998.
%
\vspace*{.5em}

\noindent{\em Writing for Computer Science}. Justin Zobel. Second Edition,  ISBN--10: 1852338024, ISBN--13:
978--1852338022, 270 pages, 2004.

\noindent Along with reading the required textbook, you may be invited to study
additional articles from a wide variety of conference proceedings, scientific
journals, and the popular press.

\vspace*{-.5em}

\subsection*{Course Policies}

\subsubsection*{Grading}

The grade that a student receives in this class will be based on the following categories. All of these percentages are
approximate and, if the need to do so presents itself, it is possible for the course instructor to change the assigned
percentages during the academic semester.

\begin{center}
  \begin{tabular}{ll}
    Class Participation        & 5\%  \\
    Mastery Quizzes            & 10\% \\
    Midterm Examination        & 10\% \\
    Final Examination          & 15\% \\
    Practical Assignments      & 15\% \\
    Laboratory Assignments     & 30\% \\
    Design Portfolio           & 15\%
  \end{tabular}
\end{center}

\vspace*{-.05in}

\noindent
These grading categories have the following definitions:

\vspace*{-.05in}

\begin{itemize}

  \item {\em Class Participation\/}: All students are required to actively
    participate during all of the course sessions. Your participation will take
    forms such as answering questions about the reading assignments, asking
    constructive questions of group members, giving presentations, and leading a
    discussion. You also must regularly participate in the discussions in the
    course's Slack workspace. A student may request feedback on and will receive
    a final grade for this category.

  \item {\em Mastery Quizzes\/}: The two quizzes will cover all of the material
    in their associated module(s). While the second quiz is not cumulative, it
    will assume that a student has a basic understanding of the material that
    was the focus of the first quiz. The date for each of the quizzes will be
    announced at least one week in advance of the scheduled date. Unless prior
    arrangements are made with the course instructor, all students will be
    expected to take these two quizzes on the scheduled date and to complete the
    quizzes in the stated period of time.

  \item {\em Midterm Examination\/}: The midterm is an hour-long cumulative test
    covering all of the material from the class, practical, and laboratory
    sessions, as outlined on the review sheet. Unless prior arrangements are
    made with the course instructor, all students will be expected to take this
    test on the scheduled date and complete the test in the stated period of
    time.

  \item {\em Final Examination\/}: The final examination is a three-hour
    cumulative test. By enrolling in this course, students agree that, unless
    there are severe extenuating circumstances, they will take the final
    examination at the date and time stated on the first page of the syllabus.

  \item {\em Practical Assignments\/}: Graded on a credit/no-credit basis, these
    assignments allow students to practice the technical skills that they
    learned in previous class and laboratory sessions.

  \item {\em Laboratory Assignments\/}: These assignments invite students to
    explore different techniques for designing, implementing, evaluating, and
    documenting software solutions to challenging problems connect to the
    creation of real-world web sites. These assignments will invite students to
    use the languages and technologies of web development to create and evaluate
    web sites. To ensure that students are ready to develop software in both
    other classes at Allegheny and after graduation, students will complete
    assignments both on an individual basis and in teams. When teamwork is
    required, the instructor will often assign individuals to teams.

  \item {\em Design Portfolio\/}: This long-term project will furnish you with
    the description of a web development task and ask you to specify, design,
    implement, test, document, revise, and release a correct and carefully
    evaluated web site. Completion of the design portfolio will require you to
    apply all of the knowledge and skills that you are learning during the
    semester to solve technical problems and document your solutions and
    experiences. In addition to demonstrating the mastery of the technical and
    professional skills in the web development field, students should also plan
    to publicly release their web site and all of its source code.

\end{itemize}

\subsubsection*{Assignment Submission and Evaluation}

All assignments will have a stated due date. Electronic versions of the
laboratory, practical, and design portfolio assignments must be submitted to a
student's GitHub repository; students will learn how to use version control with
GitHub during the laboratory and practical sessions. No credit will be awarded
for any course work that is not submitted to your GitHub repository with the
required name. Unless specified otherwise, all of assignments must be turned in
at the beginning of the session that is one week after the day the assignment
was released. Unless special arrangements are made with the course instructor,
no work will be accepted after the published deadline.

Using a report that the instructor shares with you through the commit log in
GitHub, you will privately received a grade for and feedback on each assignment.
Your grade will be a function of whether or you not completed correct work and
submitted it by the deadline. Other factors (e.g., the quality of your source
code and technical writing) will also influence your assignment grade.

\subsubsection*{Course Attendance}

It is mandatory for all students to attend all of the class, practical, and
laboratory sessions. If, due to extenuating circumstances, you will not be able
to attend a session, then, whenever possible, please see the course instructor
at least one week in advance to describe your situation. Students who miss more
than five unexcused sessions will have their final grade in the course reduced
by one letter grade. Students who miss more than ten of the aforementioned
events will fail the course.

\subsubsection*{Use of Laboratory Facilities}

Throughout the semester, we will employ many different software tools that
computer scientists use during the design, implementation, and evaluation of web
sites. Since it is unlikely that an unmodified computer will have the software
that correctly supports the completion of the laboratory assignments, unless
there are extenuating circumstances, students struggling with computer setup
must complete all of their work for this course while using the department's
laboratory facilities.

\subsubsection*{Class Preparation}

In order to minimize confusion and maximize learning, students must invest time
to prepare for the class discussions, lectures, and practical sessions. During
the class periods, the course instructor will often pose challenging questions
that could require group discussion, the creation of a web site or image, a vote
on a thought-provoking issue, or a group presentation. Only those students who
have prepared for class by reading the assigned material and reviewing the
current laboratory and practical assignments will be able to effectively
participate in these discussions.

More importantly, only prepared students will be able to acquire the knowledge
and skills that they need to be successful in this course, subsequent courses,
and the field of computer science. In order to help students remain organized
and to effectively prepare for classes, the course instructor will maintain a
class schedule with reading assignments and presentation slides. During the
class sessions students will also be required to download, use, and modify
programs and data sets that are made available through means such as the course
web site and a GitHub repository.

\subsubsection*{Seeking Assistance}

Students who are struggling to understand the knowledge and skills developed in
a class, laboratory, or practical session are encouraged to seek assistance from
the course instructor, the teaching assistants, or the departmental tutors.
Throughout the semester, students should, within the bounds of the Honor Code,
ask and answer questions on the Slack workspace for our course; please request
assistance from the instructor, teaching assistants, and tutors first through
Slack before sending an email. Students who need the course instructor's
assistance must schedule a meeting through \instructorpronoun{} web site and
come to the meeting with all of the details needed to discuss their question.

\subsubsection*{Using Email}

Although we will primarily use Slack for class communication, I will sometimes
use email to send announcements about important matters such as changes in the
schedule. It is your responsibility to check your email at least once a day and
to ensure that you can reliably send and receive emails. This class policy is
based on the statement about the use of email that appears in {\em The Compass},
the College's student handbook; please see the instructor if you do not have
this handbook.

\subsubsection*{Honor Code}

The Academic Honor Program that governs the entire academic program at Allegheny
College is described in the Allegheny Academic Bulletin. The Honor Program
applies to all work that is submitted for academic credit or to meet non-credit
requirements for graduation at Allegheny College. This includes all work
assigned for this class (e.g., examinations, laboratory assignments, and the
design portfolio). All students who have enrolled in the College will work under
the Honor Program. Each student who has matriculated at the College has
acknowledged the following pledge:

\vspace*{-.11in}
%
\begin{quote}
%
  I hereby recognize and pledge to fulfill my responsibilities, as defined in
  the Honor Code, and to maintain the integrity of both myself and the College
  community as a whole.
%
\end{quote}
%
\vspace*{-.11in}

\noindent It is understood that an important part of the learning process in any
course, and particularly one in computer science, derives from thoughtful
discussions with teachers and fellow students. Such dialogue is encouraged.
However, it is necessary to distinguish carefully between the student who
discusses the principles underlying a problem with others and the student who
produces assignments that are identical to, or merely variations on, someone
else's work. While it is acceptable for students in this class to discuss their
source code, images, and reports with their classmates, deliverables that
are nearly identical to the work of others will be taken as evidence of
violating the \mbox{Honor Code}.

\subsubsection*{Disability Services}

The Americans with Disabilities Act (ADA) is a federal anti-discrimination
statute that provides comprehensive civil rights protection for persons with
disabilities. Among other things, this legislation requires all students with
disabilities be guaranteed a learning environment that provides for reasonable
accommodation of their disabilities. Students with disabilities who believe they
may need accommodations in this class are encouraged to contact Disability
Services at 332--2898. Disability Services is part of the Learning Commons and
is located in Pelletier Library. Please do this as soon as possible to ensure
that approved accommodations are implemented in a timely fashion.

\subsection*{Welcome to an Adventure in Web Development}

In reference to software, Frederick P.\ Brooks, Jr.\ wrote in chapter one of
{\em The Mythical Man Month}, ``The magic of myth and legend has come true in
our time.'' Web sites are a pervasive aspect of our society that changes how we
think and act. Efficient and correct web sites also have the potential to
positively influence the lives of many people. Moreover, the design,
implementation, evaluation, and documentation of web-based software are exciting
and rewarding activities! At the start of this class, I invite you to pursue,
with great enthusiasm and vigor, this adventure in web development.

\end{document}
